---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BuildRWeek2Assign0207

<!-- badges: start -->
<!-- badges: end -->

The goal of BuildRWeek2Assign0207 is to read Data is taken from 2013-2015 US National Highway Traffic Safety Administration's Fatality Analysis Reporting System,which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

It is possible to request a summary report or a Map by State wiht fatalities for a given year

## Installation

You can install the released version of BuildRWeek2Assign0207 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("BuildRWeek2Assign0207")
```

## Filenames
Three data files are available in this package. They are in the inst\extdata folders 
accident_2013.csv.bz2
accident_2014.csv.bz2
accident_2015.csv.bz2

## Example-text summary report request

This is a basic example which shows you how to solve a common problem:

```{r example}
library(BuildRWeek2Assign0207)
fars_summarize_years(c(2013,2014))

```

## Example: Map of Fatalities by State for a Given Year

```{r  messages = FALSE, eval = TRUE}
fars_map_state(1,2015)
```


