---
title: "fars_functions"
author: Mary Mangraviti
date: "2021-02-16"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars_functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BuildRWeek2Assign0207)
```
## Oveview
Data in this package is taken from 2013-2015 US National Highway Traffic Safety Administration's Fatality Analysis Reporting System,
which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.


## Filenames
Three data files are available in this package. They are in the inst\extdata folders 
accident_2013.csv.bz2
accident_2014.csv.bz2
accident_2015.csv.bz2

## Summary Reports for a single year
The user can get a summary report for one year for 2013-2015 inclusive

``` {r  messages = FALSE, eval = TRUE}
fars_summarize_years(2013)
```


## Summary Reports for a multiple years
The user can get a summary report for a vector of years for 2013-2015 inclusive

```{r  messages = FALSE, eval = TRUE}
fars_summarize_years(c(2013,2014))
```

## Maps of Incidents by state 
The user can also produce a map of incidents by Year for An integer State Numbr

```{r  messages = FALSE, eval = TRUE}
fars_map_state(1,2015)
```
